Distortion corrected kernel density estimate on Riemannian manifolds

### 2022-10-31 paper/paper.tex
post merge commit

\autoref{fig:electricityoutliers} shows the electricity usage data of three households for density estimation both with and without distortion correction respectively, with the top one being the most typical household with the highest density and the bottom two being the top two outliers with the lowest densities.
The typical households in the top row are similar except that there are a few spikes for household \(1472\) when using KDE. As for the anomalies, distortion corrected KDE tends to capture the unusual electricity demand when the usage is very low or high in volume. It could also capture the unusual usage pattern when there are sudden spikes in ID 3243 or very high base electricity usage for the middle time periods in ID 2838. In contrast, KDE without distortion correction is more sensitive to spikes even when the spikes happen in a certain time window in 7049, or when the usage has an obvious time-of-week pattern with a few low electricity usage periods.

>>>>

\autoref{fig:electricityoutliers} shows the electricity usage data of three households for density estimation both with and without distortion correction respectively, with the top one being the most typical household with the highest density and the bottom two being the top two outliers with the lowest densities.
The typical households in the top row are similar except that there are a few spikes for household \(1472\) (selected as most typical when using KDE without distortion correction). As for the anomalies, distortion corrected KDE tends to capture instance of unusual electricity demand where usage is very low with some sudden spikes such as ID 3243 or households with a very high baseline electricity usage only across a sub-period of time such as ID 2838. In contrast, KDE without distortion correction can select households that do not exhibit anomalous behavior at all, such as household 5146 and the selection of such houesholds as anomalies may be an artefact of distortion induced by a dimension reduction algorithm.
